---
title: "Template" # this doesn't show anywhere, normally this would produce an H1 header at the top of the rendered page. This has been overriden in the css.
pagetitle: "Something meaningful" # this appears in the tab
output:
  html_document:
    code_folding: show # allows toggling of showing and hiding code. Remove if not using code.
    code_download: true # allows the user to download the source .Rmd file. Remove if not using code.
    includes:
      after_body: footer.html # include a custom footer.
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
---

## Start with a level two header

:::note
This is a note.
:::

:::question
This is a question.
:::

:::flag
This is a flag.
:::

The following can be used for erroneous code, incorrect output, and proper code with correct output. The otuput at the moment is a little jarring. We'll fix this.    

```{r class.source="bg-danger", class.output="bg-warning"}
mtcars[1:5, "mpg"]
```

```{r df-drop-ok, class.source="bg-success"}
mtcars[1:5, "mpg", drop = FALSE]
```

All code is shown by default. You can change this default in the YAML by swapping `code_folding: show` to `code_folding: hide`.

To override this default, when `code_folding: show` is true:

```{r class.source = 'fold-hide'}
2  # code is hidden initially
```

And when `code_folding: hide` is true:

```{r class.source = 'fold-show'}
2  # code is hidden initially
```